---
params:
  current_week:
  current_season:

title: "Panera Sucks"
date: "Updated: `r Sys.time()`"
output:
  rmdformats::html_clean:
    highlight: kate
    toc_depth: 2
    toc_float: 
      collapsed: false
---

```{r, echo = FALSE}
id <- 1094681 # League ID
league_name <- "Panera Sucks"
first_season <- 2012
curr_season <- params$current_season # Current season/year
curr_week <- params$current_week # Current week
```

```{css, echo = FALSE}
h1, h2, h3 {
  font-weight: bold;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.align = "center")
options(knitr.kable.NA = "")
```

```{r, warning = FALSE, message = FALSE}
library(ffscrapr)
library(nflfastR)
library(nflreadr)
library(tidyverse)
library(kableExtra)
library(ggthemes)
library(formattable)
library(RColorBrewer)
library(plotly)
library(shiny)
```

# Weekly Reports

* 2022 Season
  * [Week 1](weekly_reports/2022/week1/)
  * [Week 2](weekly_reports/2022/week2/)
  * [Week 3](weekly_reports/2022/week3/)
  * [Week 4](weekly_reports/2022/week4/)
  * [Week 5](weekly_reports/2022/week5/)
  * [Week 6](weekly_reports/2022/week6/)
  * [Week 7](weekly_reports/2022/week7/)
  * [Week 8](weekly_reports/2022/week8/)
  * [Week 9](weekly_reports/2022/week9/)
  * [Week 10](weekly_reports/2022/week10/)
  * [Week 11](weekly_reports/2022/week11/)
  * [Week 12](weekly_reports/2022/week12/)
  * [Week 13](weekly_reports/2022/week13/)

# League History

* [League History](league_history/)

```{r}
# League objects for seasons 2012 to curr_season
all_leagues <- first_season:curr_season %>%
  map(function(x) {
    espn_connect(
      season = x,
      league_id = id,
      swid = Sys.getenv("TAN_SWID"),
      espn_s2 = Sys.getenv("TAN_ESPN_S2")
    )
  })  

curr_league <- all_leagues[[length(all_leagues)]]

# Pretty round
pr <- function(x, digits = 2) {
  format(round(x, digits), nsmall = digits)
}

# Team colors
cols_8 <- brewer.pal(8, "Set2")
cols_dark_8 <- brewer.pal(8, "Dark2")

# Position factor levels
pos_lvl <- c("QB", "RB", "WR", "TE", "DST", "K")

# Position colors
pos_col <- c("#FF8181", "#A9D08E", "#94BEE4", "#FFD966", "#C7A1E3", "#F4B084")

position_col <- bind_cols(pos = pos_lvl, pos_col = pos_col)

# Lineup slot factor levels
slot_lvl <- c("QB", "RB", "WR", "TE", "FLEX", "DST", "K", "TOTAL")
slot_col <- c("#FF8181", "#A9D08E", "#94BEE4", "#FFD966",
                     "#B6B6B6", "#C7A1E3", "#F4B084", "#FFFF00")

lineup_slot_col <- bind_cols(lineup_slot = slot_lvl, slot_col = slot_col)

# Team colors
nfl_team_col <- tribble(
  ~team, ~team_bg,
  "ARI", "#97233F",
  "ATL", "#A71930",
  "BAL", "#241773",
  "BUF", "#00338D",
  "CAR", "#0085CA",
  "CHI", "#F26522",
  "CIN", "#FB4F14",
  "CLE", "#22150C",
  "DAL", "#0C264C",
  "DEN", "#FB4F14",
  "DET", "#046EB4",
  "GBP", "#24423C",
  "HOU", "#00143F",
  "IND", "#003D79",
  "JAC", "#D8A328",
  "KCC", "#CA2430",
  "LAC", "#2072BA",
  "LAR", "#95774C",
  "MIA", "#0091A0",
  "MIN", "#4F2E84",
  "NEP", "#0A2342",
  "NOS", "#A08A58",
  "NYG", "#192E6C",
  "NYJ", "#203731",
  "OAK", "#000000",
  "PHI", "#014A53",
  "PIT", "#FFC20E",
  "SEA", "#7AC142",
  "SFO", "#C9243F",
  "TBB", "#D40909",
  "TEN", "#4095D1",
  "WAS", "#FFC20F"
)

# All seasons
all_franchises <- all_leagues %>%
  map_dfr(function(x) {
    bind_cols(season = as.numeric(x$season), ff_franchises(x))
  })
  
all_sched <- all_leagues %>%
  map_dfr(function(x) {
    bind_cols(season = as.numeric(x$season), ff_schedule(x))
  })

all_standings <- all_leagues %>%
  map_dfr(function(x) {
    bind_cols(season = as.numeric(x$season), ff_standings(x))
  })


# all_lineups <- all_leagues %>%
#   map_dfr(function(x) {
#     bind_cols(season = as.numeric(x$season), ff_starters(x))
#   })

#test <- ff_playerscores(curr_league)
#test2 <- ff_scoringhistory(curr_league)

# Current season league objects
franchises <- all_franchises %>%
  filter(season == curr_season) %>%
  mutate(franchise_name = fct_reorder(franchise_name, franchise_id, min))

franchise_color <- franchises %>%
  select(franchise_id, franchise_name) %>%
  bind_cols(fr_col = cols_8, fr_col_dark = cols_dark_8)

lineups <- ff_starters(curr_league, week = curr_week) %>%
  mutate(franchise_name = fct_reorder(franchise_name, franchise_id, min),
         pos = factor(pos, levels = pos_lvl)) %>%
  left_join(franchise_color, by = c("franchise_id", "franchise_name")) %>%
  mutate(clean_name = dp_clean_names(player_name, lowercase = TRUE))

schedule <- ff_schedule(curr_league) %>%
  left_join(franchise_color) %>%
  left_join(franchise_color, by = c("opponent_id" = "franchise_id"))

```

# Current Standings (`r params$current_season` Season, Week `r curr_week`)

## Regular Standings
```{r}
standings <- all_standings %>%
  filter(season == curr_season) %>%
  arrange(desc(h2h_wins), desc(points_for)) %>%
  mutate(rank = row_number(),
         points_for = color_bar("lightgreen")(comma(points_for)),
         points_against = color_bar("pink")(comma(points_against))) %>%
  left_join(franchise_color, by = c("franchise_id", "franchise_name"))

standings %>%
  mutate(h2h_winpct = round(h2h_winpct * 100, 1)) %>%
  select(rank, franchise_name, h2h_wins, h2h_losses, h2h_ties, h2h_winpct, points_for, points_against) %>%
  kbl(col.names = c("Rank", "Franchise", "Wins", "Losses", "Ties", "Win %", "Points For", "Points Against"),
      escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2, background = standings$fr_col)
```

```{r}
weekly_records <- schedule %>%
  filter(week <= curr_week) %>%
  select(week, franchise_id, franchise_name.x, fr_col.x, franchise_score, opponent_score, result) %>%
  mutate(
    W = if_else(result == "W", 1, 0),
    L = if_else(result == "L", 1, 0),
    T = if_else(result == "T", 1, 0)
  ) %>%
  select(-result) %>%
  group_by(franchise_id, franchise_name.x, fr_col.x) %>%
  mutate(
    wins = cumsum(W),
    losses = cumsum(L),
    ties = cumsum(T),
    record = paste(wins, losses, ties, sep = "-"),
    points_for = cumsum(franchise_score),
    points_against = cumsum(opponent_score),
  ) %>%
  select(-c(W, L, T, franchise_score, opponent_score)) %>%
  arrange(week, desc(wins), desc(points_for)) %>%
  group_by(week) %>%
  mutate(weekly_rank = row_number())

fig <- plot_ly(weekly_records,
  x = ~week,
  y = ~weekly_rank,
  split = ~franchise_name.x,
  type = "scatter",
  mode = "line",
  color = ~franchise_name.x,
  colors = cols_dark_8
  ) %>%
  layout(
    title = "Weekly Standings",
    xaxis = list(
      title = "",
      ticktext = as.list(paste("Week", seq(1, curr_week))),
      tickvals = as.list(seq(1, curr_week)),
      tickmode = "array"
      ),
    yaxis = list(
      title = "",
      autorange = "reversed",
      ticktext = as.list(scales::ordinal(seq(1, 8))),
      tickvals = as.list(seq(1, 8)),
      tickmode = "array"
    ),
    showlegend = FALSE,
    hovermode = "x"
    )

div(fig, align = "center")
```


## All-Play Standings

`All-Play` is your record if you played all other teams every single week.

```{r}
allplay_standings <- standings %>%
  arrange(desc(allplay_wins), desc(points_for)) %>%
  mutate(rank = row_number())

allplay_standings %>%
  mutate(allplay_winpct = round(allplay_winpct * 100, 1)) %>%
  select(rank, franchise_name, allplay_wins, allplay_losses, allplay_winpct) %>%
  kbl(col.names = c("Rank", "Franchise", "All-Play Wins", "All-Play Losses", "All-Play Win %"),
      escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2, background = allplay_standings$fr_col)
```
