---
params:
  current_week:
  current_season:
    
title: "League History"
subtitle: "Panera Sucks"
date: "Updated: `r Sys.time()`"
output:
  rmdformats::html_clean:
    highlight: kate
    toc_depth: 2
    toc_float: 
      collapsed: false
---

[Back](../index.html)

```{r, echo = FALSE}
id <- 1094681 # League ID
league_name <- "Panera Sucks"
first_season <- 2012
curr_season <- params$current_season # Current season/year
curr_week <- params$current_week # Current week
oldest_lineup_season <- 2018
```

<!-- https://mbounthavong.com/blog/2022/7/30/hosting-a-r-markdown-html-file-on-a-github-page -->

```{css, echo = FALSE}
h1, h2, h3 {
  font-weight: bold;
}
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.align = "center")
options(knitr.kable.NA = "")
```

```{r, warning = FALSE, message = FALSE}
library(ffscrapr)
library(nflfastR)
library(nflreadr)
library(tidyverse)
library(kableExtra)
library(ggthemes)
library(formattable)
library(RColorBrewer)
library(plotly)
library(shiny)
```

```{r}
# League objects for seasons 2013 to curr_season
all_leagues <- first_season:curr_season %>%
  map(function(x) {
    espn_connect(
      season = x,
      league_id = id,
      swid = Sys.getenv("TAN_SWID"),
      espn_s2 = Sys.getenv("TAN_ESPN_S2")
    )
  })  

curr_league <- all_leagues[[length(all_leagues)]]

# Pretty round
pr <- function(x, digits = 2) {
  format(round(x, digits), nsmall = digits)
}

# Team colors
cols_8 <- brewer.pal(8, "Set2")
cols_dark_8 <- brewer.pal(8, "Dark2")

# Position factor levels
pos_lvl <- c("QB", "RB", "WR", "TE", "DST", "K")

# Position colors
pos_col <- c("#FF8181", "#A9D08E", "#94BEE4", "#FFD966", "#C7A1E3", "#F4B084")

position_col <- bind_cols(pos = pos_lvl, pos_col = pos_col)

# Lineup slot factor levels
slot_lvl <- c("QB", "RB", "WR", "TE", "FLEX", "DST", "K", "TOTAL", "BE", "IR")
slot_col <- c("#FF8181", "#A9D08E", "#94BEE4", "#FFD966",
              "#B6B6B6", "#C7A1E3", "#F4B084", "#FFFF00", "#a4a4a4", "#ff0000")

lineup_slot_col <- bind_cols(lineup_slot = slot_lvl, slot_col = slot_col)

# Medal colors (gold, silver, bronze)
medals <- c("#FFD700", "#C0C0C0", "#CD7F32")


# Team colors
nfl_team_col <- tribble(
  ~team, ~team_bg,
  "ARI", "#97233F",
  "ATL", "#A71930",
  "BAL", "#241773",
  "BUF", "#00338D",
  "CAR", "#0085CA",
  "CHI", "#F26522",
  "CIN", "#FB4F14",
  "CLE", "#22150C",
  "DAL", "#0C264C",
  "DEN", "#FB4F14",
  "DET", "#046EB4",
  "GBP", "#24423C",
  "HOU", "#00143F",
  "IND", "#003D79",
  "JAC", "#D8A328",
  "KCC", "#CA2430",
  "LAC", "#2072BA",
  "LAR", "#95774C",
  "MIA", "#0091A0",
  "MIN", "#4F2E84",
  "NEP", "#0A2342",
  "NOS", "#A08A58",
  "NYG", "#192E6C",
  "NYJ", "#203731",
  "OAK", "#000000",
  "PHI", "#014A53",
  "PIT", "#FFC20E",
  "SEA", "#7AC142",
  "SFO", "#C9243F",
  "TBB", "#D40909",
  "TEN", "#4095D1",
  "WAS", "#FFC20F"
)

# All seasons
all_franchises <- all_leagues %>%
  map_dfr(function(x) {
    bind_cols(season = as.numeric(x$season), ff_franchises(x))
  })
  
all_sched <- all_leagues %>%
  map_dfr(function(x) {
    bind_cols(season = as.numeric(x$season), ff_schedule(x))
  })

all_standings <- all_leagues %>%
  map_dfr(function(x) {
    bind_cols(season = as.numeric(x$season), ff_standings(x))
  })

# all_rosters <- all_leagues %>%
#   map_dfr(function(x) {
#     bind_cols(season = as.numeric(x$season), ff_rosters(x))
#   })

# all_draft <- all_leagues %>%
#   map_dfr(function(x) {
#     bind_cols(season = as.numeric(x$season), ff_draft(x))
#   })

all_lineups <- all_leagues %>%
  keep(function(x) {
    x$season >= oldest_lineup_season
  }) %>%
  map_dfr(function(x) {
    bind_cols(season = as.numeric(x$season), ff_starters(x))
  })

franchise_id_user <- all_franchises %>%
  select(season, franchise_id, user_name) %>%
  mutate(
    user_name = str_to_title(user_name),
    user_name = case_when(
      user_name == "Dan H" ~ "Dan Hartman",
      user_name == "Justin Pattison Justin Pattison" ~ "Justin Pattison",
      TRUE ~ user_name
    )
  ) %>%
  select(season, franchise_id, user_name)

all_standings <- all_standings %>%
  left_join(franchise_id_user)

# Current season league objects
franchises <- all_franchises %>%
  filter(season == curr_season) %>%
  mutate(franchise_name = fct_reorder(franchise_name, franchise_id, min))

franchise_color <- franchises %>%
  select(franchise_id, franchise_name) %>%
  bind_cols(fr_col = cols_8, fr_col_dark = cols_dark_8)

lineups <- all_lineups %>%
  mutate(lineup_slot = if_else(lineup_slot == "RB/WR/TE", "FLEX", lineup_slot)) %>%
  left_join(lineup_slot_col) %>%
  mutate(pos = factor(pos, levels = pos_lvl),
         lineup_slot = factor(lineup_slot, levels = slot_lvl)) %>%
  left_join(franchise_id_user, by = c("season", "franchise_id")) %>%
  mutate(clean_name = dp_clean_names(player_name, lowercase = TRUE))

schedule <- all_sched %>%
  left_join(franchise_color) %>%
  left_join(franchise_color, by = c("opponent_id" = "franchise_id"))

```

# Historic Rankings

## Cumulative Standings

Cumulative standings from `r first_season` to `r curr_season`.

```{r}
tot_seasons <- franchise_id_user %>%
  group_by(user_name) %>%
  summarize(seasons = n())

all_records <- all_sched %>%
  filter(!is.na(result)) %>%
  left_join(franchise_id_user) %>%
  select(season, week, franchise_id, user_name, franchise_score, opponent_score, result) %>%
  mutate(
    W = if_else(result == "W", 1, 0),
    L = if_else(result == "L", 1, 0),
    T = if_else(result == "T", 1, 0)
  ) %>%
  select(-result) %>%
  group_by(season, user_name) %>%
  summarize(
    h2h_wins = sum(W),
    h2h_losses = sum(L),
    h2h_ties = sum(T),
    points_for = sum(franchise_score),
    points_against = sum(opponent_score),
  )

cumulative_standings <- all_records %>%
  group_by(user_name) %>%
  summarize(
    h2h_wins = sum(h2h_wins),
    h2h_losses = sum(h2h_losses),
    h2h_ties = sum(h2h_ties),
    points_for = sum(points_for),
    points_against = sum(points_against),
  ) %>%
  arrange(desc(h2h_wins), desc(points_for)) %>%
  mutate(
    h2h_winpct = (h2h_wins + h2h_ties / 2) / (h2h_wins + h2h_losses + h2h_ties),
    points_for = color_bar("lightgreen")(comma(points_for)),
    points_against = color_bar("pink")(comma(points_against)),
    rank = row_number()
  ) %>%
  left_join(tot_seasons)

cumulative_standings %>%
  mutate(h2h_winpct = round(h2h_winpct * 100, 1)) %>%
  select(rank, user_name, seasons, h2h_wins, h2h_losses, h2h_winpct, points_for, points_against) %>%
  kbl(
    digits = 2,
    col.names = c("Rank", "Owner", "Total Seasons", "Total Wins", "Total Losses", "Win %", "Total Points For", "Total Points Against"),
    escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Average Standings

Average statistics for completed seasons:

```{r}
tot_prior_seasons <- franchise_id_user %>%
  filter(season < curr_season) %>%
  group_by(user_name) %>%
  summarize(seasons = n())

avg_standings <- all_records %>%
  filter(season < curr_season) %>%
  group_by(user_name) %>%
  summarize(across(where(is.numeric), mean)) %>%
  mutate(
    h2h_winpct = (h2h_wins + h2h_ties / 2) / (h2h_wins + h2h_losses + h2h_ties)
  ) %>%
  arrange(desc(h2h_wins), desc(points_for)) %>%
  ungroup() %>%
  mutate(
    points_for = color_bar("lightgreen")(comma(points_for)),
    points_against = color_bar("pink")(comma(points_against)),
    rank = row_number()
  ) %>%
  left_join(tot_prior_seasons)

avg_standings %>%
  mutate(h2h_winpct = round(h2h_winpct * 100, 1)) %>%
  select(rank, user_name, seasons, h2h_wins, h2h_losses, h2h_winpct, points_for, points_against) %>%
  kbl(
    digits = 2,
    col.names = c("Rank", "Owner", "Full Seasons", "Avg. Wins", "Avg. Losses", "Win %", "Avg. Points For", "Avg. Points Against"),
    escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## League Finishes

```{r}
avg_league_finish <- all_standings %>%
  filter(season < curr_season) %>% 
  group_by(user_name) %>%
  summarize(avg_finish = mean(league_rank))

league_finishes <- all_standings %>%
  filter(season < curr_season) %>% 
  group_by(user_name, league_rank) %>%
  summarize(n = n()) %>%
  arrange(league_rank) %>%
  pivot_wider(
    id_cols = user_name,
    names_from = league_rank, names_prefix = "R",
    values_from = n
  ) %>%
  left_join(avg_league_finish) %>%
  ungroup() %>%
  arrange(desc(R1), desc(R2), desc(R3)) %>%
  mutate(rank = rank(-R1, ties.method = "min"))

league_finishes %>%
  select(rank, user_name, starts_with("R"), avg_finish) %>%
  kbl(
    digits = 2,
    col.names = c("Rank", "Owner", scales::ordinal(seq(1:max(all_standings$league_rank))), "Avg."),
    escape = F,
    caption.short = "* Inactive"
    ) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(13, color = "white", background = spec_color(league_finishes$avg_finish, end = 0.9,  direction = -1))
```

# All Time Awards

## Highest and Lowest Scoring Franchise
```{r}
ecdf_pctile <- function(x, val) ecdf(x)(val)

all_sched_played <- all_sched %>%
  filter(!is.na(result)) %>%
  left_join(franchise_id_user) %>%
  arrange(desc(franchise_score))

all_team_scores <- all_sched_played %>%
  mutate(
    raw_pctile = ecdf_pctile(all_sched_played$franchise_score, franchise_score),
    raw_pctile = if_else(franchise_score == min(franchise_score), 0, raw_pctile),
    score_pctile = round(raw_pctile * 100, 1),
    pctile_col = case_when(
      score_pctile == 100 ~ "#E5CC80",
      score_pctile >= 99 ~ "#E268A8",
      score_pctile >= 95 ~ "#FF8000",
      score_pctile >= 75 ~ "#A335EE",
      score_pctile >= 50 ~ "#0070FF",
      score_pctile >= 25 ~ "#00C600",
      score_pctile == 0  ~ "#000000",
      TRUE ~ "#666666"
      ))  %>%
  arrange(desc(franchise_score)) %>%
  mutate(rank = rank(-franchise_score, ties.method = "min"))

team_high <- all_sched_played %>% slice_head(n = 1)
team_low <- all_sched_played %>% slice_tail(n = 1)

all_team_scores %>%
  select(rank, user_name, franchise_score, score_pctile, season, week) %>%
  kbl(
    col.names = c("Rank", "Owner", "Score", "Percentile", "Season", "Week"),
    escape = F
    ) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = TRUE) %>%
  column_spec(4, background = all_team_scores$pctile_col, color = "white")
```

### - Highest Scoring Franchise
The highest score was attained by **`r team_high$user_name`** with **`r pr(team_high$franchise_score)`** points in week **`r team_high$week`** of the **`r team_high$season`** season.

```{r}
if (team_high$season >= oldest_lineup_season) {
  best_lineup <- lineups %>%
    inner_join(team_high, by = c("season", "week", "user_name")) %>%
    filter(!(lineup_slot %in% c("BE", "IR"))) %>%
    arrange(lineup_slot)
  
  best_lineup %>%
    select(lineup_slot, player_name, team, player_score) %>%
    kbl(
      col.names = c("", "", "", ""),
      escape = F
      ) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, background = best_lineup$slot_col)
}
```

### - Lowest Scoring Franchise
The lowest score was achieved **`r team_low$user_name`** with **`r pr(team_low$franchise_score)`** points in week **`r team_low$week`** of the **`r team_low$season`** season.

```{r}
if (team_low$season >= oldest_lineup_season) {
  worst_lineup <- lineups %>%
    inner_join(team_low, by = c("season", "week", "franchise_id")) %>%
    filter(!(lineup_slot %in% c("BE", "IR"))) %>%
    arrange(lineup_slot)
  
  worst_lineup %>%
    select(lineup_slot, player_name, team, player_score) %>%
    kbl(
      col.names = c("", "", "", ""),
      escape = F
      ) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, background = best_lineup$slot_col)
}
```

## Starts of the Week

Since the `r oldest_lineup_season` season:

```{r}
best_starters <- lineups %>%
  filter(!(lineup_slot %in% c("BE", "IR"))) %>%
  group_by(pos) %>%
  slice_max(player_score) %>%
  left_join(nfl_team_col, by = "team") %>%
  left_join(position_col, by = c("pos"))

best_starters %>%
  select(pos, player_name, team, player_score, user_name, season, week) %>%
  kbl(col.names = c("Position", "Name", "Team", "Score", "Owner", "Season", "Week")) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, background = best_starters$pos_col)
```

## Benchwarmers of the Week

Since the `r oldest_lineup_season` season:

```{r}
best_bench <- lineups %>%
  filter(lineup_slot %in% c("BE", "IR")) %>%
  group_by(pos) %>%
  slice_max(player_score) %>%
  left_join(nfl_team_col, by = "team") %>%
  left_join(position_col, by = c("pos"))

best_bench %>%
  select(pos, player_name, team, player_score, user_name, season, week) %>%
  kbl(col.names = c("Position", "Name", "Team", "Score", "Owner", "Season", "Week")) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, background = best_bench$pos_col)
```

## Best and Worst Managers

How close were teams to their optimal lineup?

```{r}
# Best QB
max_qb <- lineups %>%
  select(-c(franchise_score, lineup_slot, projected_score, eligible_lineup_slots)) %>%
  filter(pos == "QB") %>%
  group_by(season, week, franchise_id) %>%
  arrange(desc(player_score)) %>%
  slice_max(player_score, n = 2) %>%
  mutate(slot = "QB")

# Best RB
max_rb <- lineups %>%
  select(-c(franchise_score, lineup_slot, projected_score, eligible_lineup_slots)) %>%
  filter(pos == "RB") %>%
  group_by(season, week, franchise_id) %>%
  arrange(desc(player_score)) %>%
  slice_max(player_score, n = 3) %>%
  mutate(slot = "RB")

# Best WR
max_wr <- lineups %>%
  select(-c(franchise_score, lineup_slot, projected_score, eligible_lineup_slots)) %>%
  filter(pos == "WR") %>%
  group_by(season, week, franchise_id) %>%
  arrange(desc(player_score)) %>%
  slice_max(player_score, n = 3) %>%
  mutate(slot = "WR")

# Best TE
max_te <- lineups %>%
  select(-c(franchise_score, lineup_slot, projected_score, eligible_lineup_slots)) %>%
  filter(pos == "TE") %>%
  group_by(season, week, franchise_id) %>%
  arrange(desc(player_score)) %>%
  slice_max(player_score, n = 1) %>%
  mutate(slot = "TE")

# Best DST
max_dst <- lineups %>%
  select(-c(franchise_score, lineup_slot, projected_score, eligible_lineup_slots)) %>%
  filter(pos == "DST") %>%
  group_by(season, week, franchise_id) %>%
  arrange(desc(player_score)) %>%
  slice_max(player_score, n = 1) %>%
  mutate(slot = "DST")

# Best K
max_k <- lineups %>%
  select(-c(franchise_score, lineup_slot, projected_score, eligible_lineup_slots)) %>%
  filter(pos == "K") %>%
  group_by(season, week, franchise_id) %>%
  arrange(desc(player_score)) %>%
  slice_max(player_score, n = 1) %>%
  mutate(slot = "K")

max_pos <- 
  bind_rows(max_qb, max_rb, max_wr, max_te, max_dst, max_k)

leftover <- lineups %>%
  select(-c(franchise_score, lineup_slot, projected_score, eligible_lineup_slots)) %>%
  mutate(flex = pos %in% c("RB", "WR", "TE")) %>%
  filter(flex == TRUE) %>%
  anti_join(max_pos) %>%
  group_by(season, week, franchise_id) %>%
  arrange(desc(player_score)) %>%
  slice_max(player_score, n = 2) %>%
  mutate(slot = "RB/WR/TE")

max_all <- bind_rows(max_pos, leftover) %>%
  mutate(
    slot = factor(
      slot,
      levels = c("QB", "RB", "WR", "TE", "RB/WR/TE", "DST", "K"))) %>%
  arrange(franchise_name, slot)

max_score <- max_all %>%
  group_by(season, week, franchise_id, user_name) %>%
  summarize(max_score = sum(player_score))



manager_efficiency <- lineups %>%
  distinct(season, week, franchise_id, user_name, franchise_score) %>%
  filter(season >= oldest_lineup_season) %>%
  inner_join(max_score) %>%
  mutate(score_delta = round(franchise_score - max_score, 2),
         score_pct = round(franchise_score * 100 / max_score, 1)) %>%
  arrange(desc(score_delta), desc(max_score)) %>%
  mutate(rank = rank(-score_delta, ties.method = "min"))

manager_best <- manager_efficiency %>% slice_head(n = 1)
manager_worst <- manager_efficiency %>% slice_tail(n = 1)
```

```{r}
manager_efficiency %>%
  select(rank, user_name, franchise_score, max_score, score_delta, score_pct, season, week) %>%
  kbl(
    col.names = c("Rank", "Owner", "Score", "Max Score", "Difference", "% of Max", "Season", "Week"),
    escape = F
    ) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), fixed_thead = TRUE) %>%
  column_spec(5, color = "white", background = spec_color(manager_efficiency$score_delta, end = 0.9))

if (manager_best$score_delta == 0) {
  manager_best_text <- paste0("**", manager_best$user_name, "** set a perfect line-up that scored **", manager_best$franchise_score, "** points in week **", manager_best$week, "** of the **", manager_best$season, "** season.")
} else {
  manager_best_text <- paste(manager_best$user_name, "set a line-up that scored", manager_best$franchise_score, ", a mere", abs(manager_best$score_delta), "points below their best possible line-up of", manager_best$max_score, "in week", manager_best$week, "of the", manager_best$season, "season.")
}

perfect_efficiency <- manager_efficiency %>%
  filter(score_delta == 0) %>%
  group_by(user_name) %>%
  summarize(n = n()) %>%
  arrange(desc(n)) %>%
  full_join(distinct(franchise_id_user, user_name)) %>%
  mutate(
    n = if_else(is.na(n), as.integer(0), n),
    rank = rank(-n, ties.method = "min")
  )

perfect_efficiency %>% 
  select(rank, user_name, n) %>%
    kbl(
    col.names = c("Rank", "Owner", "Perfect Lineups"),
    escape = F
    ) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(3, color = "white", background = spec_color(perfect_efficiency$n, end = 0.9))
  
```

### - Best Manager

`r manager_best_text`

### - Worst Manager

**`r manager_worst$user_name`** set a line-up that scored **`r manager_worst$franchise_score`**, a staggering **`r abs(manager_worst$score_delta)`** points below their best possible line-up of **`r manager_worst$max_score`**.

## Matchup Scores

```{r, eval = FALSE}
score_diff <- matchups %>%
  mutate(score_diff = franchise_score - opponent_score) %>%
  arrange(desc(score_diff)) %>%
  mutate(rank = row_number())

score_diff_best <- score_diff %>% slice_max(score_diff)
score_diff_worst <- score_diff %>% slice_min(score_diff)

score_diff %>%
  select(rank, franchise_name.x, franchise_name.y, score_diff) %>%
  kbl(
    col.names = c("Rank", "Winner", "Loser", "Margin of Victory"),
    escape = F
  ) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2, background = score_diff$fr_col.x) %>%
  column_spec(3, background = score_diff$fr_col.y) %>%
  column_spec(4, color = "white", background = spec_color(score_diff$score_diff, end = 0.9))
```

### - Biggest Blowout


### - Narrowest Victory


### - Better Luck Next Time!

```{r, eval = FALSE}
worst_luck <- matchups %>%
  slice_max(opponent_score)

worst_luck_wins <- schedule %>% 
  filter(week == curr_week,
         franchise_name.x != worst_luck$franchise_name.y,
         franchise_score < worst_luck$opponent_score) %>%
  nrow()
```

### - Not Even Close

```{r, eval = FALSE}
best_luck <- matchups %>%
  slice_min(franchise_score)

best_luck_wins <- schedule %>% 
  filter(week == curr_week,
         franchise_name.x != best_luck$franchise_name.x,
         franchise_score > best_luck$franchise_score) %>%
  nrow()
```

## Heavy Hitting Positions

Highest average points scored for positions that have more than one lineup slot.

```{r, eval = FALSE}
lineups_pos <- lineups %>%
  filter(!(lineup_slot %in% c("BE", "IR")), pos %in% c("QB", "RB", "WR", "TE")) %>%
  group_by(week, franchise_id, franchise_name, fr_col, pos) %>%
  arrange(desc(player_score)) %>%
  summarize(n = n(), mean_pt = mean(player_score),
            all_players = paste(player_name, paste0("(", player_score, ")"), collapse = ", "),.groups = "keep") %>%
  group_by(pos) %>%
  arrange(pos, desc(mean_pt)) %>%
  mutate(rank = row_number()) %>%
  left_join(position_col) %>%
  ungroup()

lineups_qb <- lineups_pos %>%
  filter(pos == "QB")

lineups_rb <- lineups_pos %>%
  filter(pos == "RB")

lineups_wr <- lineups_pos %>%
  filter(pos == "WR")

lineups_te <- lineups_pos %>%
  filter(pos == "TE")
```

```{r, eval = FALSE}
lineups_qb %>%
  select(rank, franchise_name, n, mean_pt, all_players) %>%
  kbl(digits = 2,
    col.names = c("Rank", "Franchise", "Number Played", "Avg. Points", "Player Names"),
    escape = F
  ) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2, background = lineups_qb$fr_col) %>%
  add_header_above(c("QB" = 5), background = "#FF8181", bold = T, align = "l")
```

```{r, eval = FALSE}
lineups_rb %>%
  select(rank, franchise_name, n, mean_pt, all_players) %>%
  kbl(digits = 2,
    col.names = c("Rank", "Franchise", "Number Played", "Avg. Points", "Player Names"),
    escape = F
  ) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2, background = lineups_rb$fr_col) %>%
  add_header_above(c("RB" = 5), background = "#A9D08E", bold = T, align = "l")
```

```{r, eval = FALSE}
lineups_wr %>%
  select(rank, franchise_name, n, mean_pt, all_players) %>%
  kbl(digits = 2,
    col.names = c("Rank", "Franchise", "Number Played", "Avg. Points", "Player Names"),
    escape = F
  ) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2, background = lineups_wr$fr_col) %>%
  add_header_above(c("WR" = 5), background = "#94BEE4", bold = T, align = "l")
```

```{r, eval = FALSE}
lineups_te %>%
  select(rank, franchise_name, n, mean_pt, all_players) %>%
  kbl(digits = 2,
    col.names = c("Rank", "Franchise", "Number Played", "Avg. Points", "Player Names"),
    escape = F
  ) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2, background = lineups_te$fr_col) %>%
  add_header_above(c("TE" = 5), background = "#FFD966", bold = T, align = "l")
```

## Highest Player Attributes

```{r, eval = FALSE}
scoring_rules <- ff_scoring(curr_league) %>%
  arrange(stat_id) %>%
  mutate(
    stat_name = case_when(
      stat_id ==   1 ~ "passingCompletions",
      stat_id ==  17 ~ "passing300YardGame",
      stat_id ==  18 ~ "passing400YardGame",
      stat_id ==  23 ~ "rushingCarries",
      stat_id ==  68 ~ "totalFumbles",
      stat_id == 106 ~ "defensiveFumblesForced",
      TRUE          ~ stat_name
    )
  ) 

addtl_stat <- tribble(
  ~nflfastr_event, ~platform, ~ff_event,
  "sack_fumbles", "espn", "totalFumbles",
  "receiving_fumbles", "espn", "totalFumbles",
  "rushing_fumbles", "espn", "totalFumbles",
)

espn_nflfastr_stat_mapping <- nflfastr_stat_mapping %>%
  filter(platform == "espn") %>%
  bind_rows(addtl_stat)
  
# Missing yardage bonuses for rushing/receiving/passing,
#   kickoff/punt return yardage
#   defensive stuff
league_rules <- scoring_rules %>%
  left_join(
    espn_nflfastr_stat_mapping,
    by = c(stat_name = "ff_event")
  ) %>%
  mutate(
    nflfastr_event = case_when(
      stat_name == "passingCompletions"     ~ "completions",
      stat_name == "rushingCarries"         ~ "carries",
      stat_name == "puntReturnTouchdown"    ~ "punt_return_touchdowns",
      stat_name == "puntReturnYards"        ~ "punt_return_yards",
      stat_name == "kickoffReturnTouchdown" ~ "kickoff_return_touchdowns",
      stat_name == "kickoffReturnYards"     ~ "kickoff_return_yards",
      stat_name == "passing300YardGame"     ~ "passing300YardGame",
      stat_name == "passing400YardGame"     ~ "passing400YardGame",
      stat_name == "rushing100YardGame"     ~ "rushing100YardGame",
      stat_name == "rushing200YardGame"     ~ "rushing200YardGame",
      stat_name == "receiving100YardGame"   ~ "receiving200YardGame",
      stat_name == "receiving200YardGame"   ~ "receiving200YardGame",
      TRUE ~ nflfastr_event
    ),
    platform = "espn"
  )

ros <- nflfastr_rosters(curr_season) %>%
  mutate(position = if_else(position == "SPEC", depth_chart_position, position)) %>%
  select(any_of(c(
    "season", "gsis_id", "sportradar_id",
    "player_name" = "full_name", "pos" = "position", "team"
  ))) %>%
  left_join(
    dp_playerids() %>%
      select("sportradar_id", "espn_id"),
    by = c("sportradar_id"),
    na_matches = "never"
  )

# offensive stats
offense <- nflfastr_weekly(seasons = curr_season, type = "offense") %>%
  select(any_of(c(
    "season", "week","player_id",
    "attempts", "carries", "completions", "interceptions", "passing_2pt_conversions", "passing_first_downs",
    "passing_tds", "passing_yards", "receiving_2pt_conversions", "receiving_first_downs",
    "receiving_fumbles", "receiving_fumbles_lost", "receiving_tds",
    "receiving_yards", "receptions", "rushing_2pt_conversions", "rushing_first_downs",
    "rushing_fumbles", "rushing_fumbles_lost", "rushing_tds", "rushing_yards",
    "sack_fumbles", "sack_fumbles_lost", "sack_yards", "sacks", "special_teams_tds",
    "targets")
  )) %>%
  pivot_longer(
    names_to = "metric",
    cols = -c("season","week","player_id")
  )

yd_bonus <- offense %>%
  filter(metric %in% c("passing_yards","rushing_yards","receiving_yards")) %>%
  rowwise() %>%
  mutate(
    threshold_1 = if_else(metric == "passing_yards", 400, 200),
    threshold_2 = if_else(metric == "passing_yards", 300, 100),
    t1 = value >= threshold_1,
    t2 = value >= threshold_2,
    metric = paste0(
      str_split(metric, "_")[[1]][1],
        if_else(t1, threshold_1, threshold_2),
        "YardGame"
      ),
    value = as.numeric(t1 | t2),
    threshold_1 = NULL,
    threshold_2 = NULL,
    t1 = NULL,
    t2 = NULL
  )

# kicking stats
kicking <- nflfastr_weekly(seasons = curr_season, type = "kicking") %>%
  select(any_of(c(
    "season","week","player_id",
    "fg_att", "fg_blocked",
    "fg_made", "fg_made_0_19", "fg_made_20_29", "fg_made_30_39",
    "fg_made_40_49", "fg_made_50_59", "fg_made_60_", "fg_made_distance",
    "fg_missed", "fg_missed_0_19", "fg_missed_20_29", "fg_missed_30_39",
    "fg_missed_40_49", "fg_missed_50_59", "fg_missed_60_", "fg_missed_distance",
    "fg_pct","pat_att", "pat_blocked", "pat_made",
    "pat_missed", "pat_pct"
  ))) %>%
  pivot_longer(
    names_to = "metric",
    cols = -c("season", "week", "player_id")
  )

# kick/punt return stats
returns <- load_pbp(seasons = curr_season) %>%
  filter(play_type %in% c("kickoff", "punt")) %>%
  mutate(
    player_id = coalesce(punt_returner_player_id, kickoff_returner_player_id)
  ) %>%
  select(season, week, player_id, play_type, return_yards, return_touchdown) %>%
  filter(!is.na(player_id)) %>%
  group_by(season, week, player_id, play_type) %>%
  summarize(return_yards = sum(return_yards),
            return_touchdowns = sum(return_touchdown), .groups = "keep") %>%
  pivot_wider(id_cols = c(season, week, player_id),
              names_from = play_type,
              names_glue = "{play_type}_{.value}",
              values_from = c(return_yards, return_touchdowns),
              values_fill = 0) %>%
  pivot_longer(
    cols = -c("season", "week", "player_id"),
    names_to = "metric"
  )



# Combine all stats
all_stats <- bind_rows(offense, yd_bonus, kicking, returns)

player_points <- ros %>%
  inner_join(all_stats, by = c(gsis_id = "player_id", "season")) %>%
  inner_join(league_rules, by = c(metric = "nflfastr_event", "pos")) %>%
  mutate(pp_stat = value * points) %>%
  group_by(season, week, gsis_id, sportradar_id) %>%
  mutate(tot_points = round(sum(pp_stat, na.rm = TRUE), 2)) %>%
  ungroup() %>%
  pivot_wider(
    id_cols = c(
      "season",
      "week",
      "gsis_id",
      "sportradar_id",
      "espn_id",
      "player_name",
      "pos",
      "team",
      "tot_points"
    ),
    names_from = metric,
    values_from = value,
    values_fill = 0,
    values_fn = max) %>%
  mutate(clean_name = dp_clean_names(player_name, lowercase = TRUE))

# lineup_pts <- lineups %>%
#   full_join()

  # mutate(
  #   team = case_when(
  #     team == "GB"  ~ "GBP",
  #     team == "JAX" ~ "JAC",
  #     team == "KC"  ~ "KCC",
  #     team == "LA"  ~ "LAR",
  #     team == "LV"  ~ "OAK",
  #     team == "NE"  ~ "NEP",
  #     team == "NO"  ~ "NOS",
  #     team == "SF"  ~ "SFO",
  #     team == "TB"  ~ "TBB",
  #     TRUE          ~ team
  #     ),
  #   player_name = case_when(
  #     player_name == "A.J. Dillon" ~ "AJ Dillon",
  #     player_name == "Allen Robinson" ~ "Allen Robinson II",
  #     player_name == "Brian Robinson" ~ "Brian Robinson Jr.",
  #     player_name == "Darrell Henderson" ~ "Darrell Henderson Jr.",
  #     player_name == "D.J. Moore" ~ "DJ Moore",
  #     player_name == "Josh Palmer" ~ "Joshua Palmer",
  #     player_name == "Melvin Gordon" ~ "Melvin Gordon III",
  #     player_name == "Michael Pittman" ~ "Michael Pittman Jr.",
  #     player_name == "Terrace Marshall" ~ "Terrace Marshall Jr.",
  #     TRUE ~ player_name
  #   )
  # )
```

```{r, eval = FALSE}
# Merging with ESPN

wk11_lineup <- lineups %>%
  filter(!is.na(projected_score), pos != "DST") %>%
  select(week, franchise_id, franchise_name, player_id, player_name, clean_name, pos, team, player_score) %>%
  mutate(player_id = as.character(player_id), src = "espn")

wk11_pts <- player_points %>%
  filter(week == curr_week) %>%
  select(week, gsis_id, sportradar_id, espn_id, player_name, clean_name, pos, team, tot_points) %>%
  mutate(src = "nflfastr")

### Step 1
# Matches by clean_name, player_id == espn_id
match_both_1 <- wk11_lineup %>%
  inner_join(wk11_pts, by = c("clean_name", "player_id" = "espn_id"))

# Non-matches
no_match_espn_1 <- wk11_lineup %>%
  anti_join(wk11_pts, by = c("clean_name", "player_id" = "espn_id"))

no_match_nflfastr_1 <- wk11_pts %>%
  anti_join(wk11_lineup, by = c("clean_name", "espn_id" = "player_id"))

### Step 2
# Matches by clean_name
match_both_2 <- no_match_espn_1 %>%
  inner_join(no_match_nflfastr_1, by = c("clean_name"))

# Non-matches
no_match_espn_2 <- no_match_espn_1 %>%
  anti_join(no_match_nflfastr_1, by = c("clean_name"))

no_match_nflfastr_2 <- no_match_nflfastr_1 %>%
  anti_join(no_match_espn_1, by = c("clean_name"))

```

### Run Forest, Run!

Team with the most rushing attempts (highest average rushing attempts including flex)

### Gotta Catch Em All

Team with the most receptions (highest average receptions including flex)

### Show Me Dem TDs

Team with the most TDs scored
